### 2016-04-13 Draft.tex
Many changes over the past week.  Mainly to the simulations and results sections.

A TTDD defines the range of detection patterns possible in an analysis.  
The most basic is an exponential TTDD, which imposes a constant first detection rate.  
Choosing another TTDD can allow for a systematic non-constant detection regime.  
For example, to model an observer effect where: (i) the observer's arrival suppresses or stimulates detectable cues, but (ii) organisms acclimate and gradually return to constant detection, a gamma TTDD could be appropriate (Figure \ref{HazardFxns}).

Increasing hazard functions result in a pdf for $T$ that has a mode away from zero; we term these TTDDs `peaked'.  
We contrast these to decreasing hazard functions with a mode at zero, which we term `non-peaked'.  
For our purposes, the exponential TTDD is neither peaked nor non-peaked.

@@

\begin{figure}[h!]\centering
\includegraphics[width=0.68\textwidth]{Hazards}
\caption{Examples of instantaneous rates of detection (hazard functions) from exponential, gamma, lognormal, and Weibull TTDDs.}
\label{HazardFxns}
\end{figure}

@@

Our analysis is motivated by point-count surveys conducted in Chippewa National Forest from 2008-2013 as part of the Minnesota Forest Breeding Bird Project (MNFB).  
The MNFB design is described in \citet{Hanowski1995}, and we summarize only essential details here.  
Single-visit time-to-first-detection point-count surveys were conducted by trained observers at a fixed set of sampling locations once annually.  
Survey durations were 10 minutes, with times to first detection for over 50 species being censored into nine intervals -- a two-minute interval followed by eight one-minute intervals.  
The relatively fine-scale interval sizes should provide more information about TTDDs than the three-interval methodology (0-3, 3-5, and 5-10 minutes) that characterizes many avian point count surveys \citep{Ralph1995}.
There was no prescribed settling-in period between the observer's arrival and the time they began observing.

@@

We construct a hierarchical model of removal-sampled point-counts in three pieces: (a) a data model incorporating binomial detection and time-to-detection pieces, (b) a detection model based upon a TTDD, and (c) an abundance model based upon an integer-valued distribution.  
Our model incorporates covariates and random effects for both abundance and detection via mixed effects linear regression.

\subsection{Data Model}
We assume that counts from different surveys are conditionally independent.  
We define $T_{sq}$ as a random variable for the first time at which an individual is detected.
We assume that detection times for individuals at any given survey are independent, identically distributed according to a TTDD with cdf $F_T(t)$ and pdf $f_T(t)$, which may depend on covariates.  
The probability of detecting an animal is thus $p_{s}^{(det)} = Pr(t_{sq} < C_I) = F_T(C_I)$ and the conditional distribution of observed detection times can be written $f_{T|det}(t|t_{sq}<C_I) = f_T(t) / F_T(C_I)$.  
Given $N_{s}$ total number animals present at a survey, the data model is:
\begin{align}\label{eq:datamodel}
n_{s}^{(obs)} &\sim \mbox{Binomial}\left(N_{s}, p_{s}^{(det)}\right)\\
\label{eq:Tsrq}T_{sq} &\sim f_{T|det}(t|t_{sq}<C_I)
\end{align}
When detection times are censored, we replace Eq. \ref{eq:Tsrq} with $\vn_{s} \sim \mbox{Multinomial}\left(n_{s}^{(obs)}, \textbf{p}_{s}\right)$, where $\textbf{p}_{s}$ is the vector of interval-specific detection probabilities obtained by partitioning the conditional cdf $F_{T|det}(t|t_{sq}<C_I)$ at the interval cutoff times.  
It follows that $\sum_{i=1}^I p_{si} = 1$.

@@

The two main elements of the detection model for $T_{sq}$ are: (i) the distributional form and (ii) the expectation function.
$T_{sq}$ should be based on non-negative continuous distributions, preferrably featuring a rate parameter than can be estimated via regression.  
In this study, we adopt TTDDs for $T_{sq}$ using the following: Exponential($\varphi_{s}$), Gamma($\alpha, \varphi_{s}$), Weibull($k, \varphi_{s}$), and Lognormal($\mu_{s}, \sigma_{det}^2$).  
Here, $\varphi_{s}$ and $\mu_{s}$ are survey-specific detection rate parameters, and we consider the shape parameters $\alpha$, $\sigma_{det}^2$, and $k$ to be constant across all surveys.

We can model detection heterogeneity by defining $F_T(t)$ as a mixture of TTDD components.  
In this study, we use interval-censored observations, so in addition to the four above TTDDs (with no mixture component), we consider partial finite-mixtures of a point mass during the first survey interval plus a component from an exponential, gamma, Weibull, or lognormal distribution.  
We define a constant mixing parameter $\gamma \in [0,1]$ for the proportion of animals not distributed according to the point mass.

We model the expectation function via mixed effects linear regression.  
For exponential, gamma, and Weibull TTDDs, we model: $\log(\varphi_{s}) = \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D$, where $\textbf{X}_{s}^D$ are covariates, $\boldsymbol{\beta}^D$ is a vector of fixed effects, $\textbf{Z}_{s}^D$ specify random effect levels, $\xi_i^D \overset{ind}{\sim} N(0,\sigma_{D[i]}^2)$ are random effects, with $\sigma_{D[i]}^2$ denoting the variance associated with $\xi_i^D$.  
This regression is equivalent to modeling the log of the expected time-to-detection, which is inversely related to the detection rate.  
For the lognormal distribution, we fit the regression model to $-\mu_{s}$.  
%Thus, the link functions in our detection model are:
%\begin{alignat}{3}
%&\text{Exponential:\;} &&\log(\varphi_{s}) &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}])\\
%&\text{Gamma:} &&\log(\varphi_{s}) &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}]) + \log(\alpha)\\
%&\text{Weibull:}  &&\log(\varphi_{s}) &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}]) + \log\left(\Gamma\left(1 + 1/k\right)\right)\\
%&\text{Lognormal:} &&-\mu_{s} &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}]) + \sigma_{det}^2/2
%\end{alignat}

Combining the distribution and expectation function for $T_{s}$, we can describe a partial-mixture TTDD cdf as:
\[F_T(t|\textbf{X}_{s}^D, \textbf{Z}_{s}^D, \boldsymbol{\theta}) = (1-\gamma)\mathbb{I}(t>0) + \gamma F_{T1}(t|\textbf{X}_{s}^D, \textbf{Z}_{s}^D, \boldsymbol{\theta})\]
where $F_{T1}$ is the cdf of the non-point-mass component and $\boldsymbol{\theta}$ is a vector of parameters appropriate to $F_{T1}$.  
Note that parameters in a mixture TTDD do not share the exact same interpretation as equivalent parameters from a non-mixture TTDD, since they only pertain to the $\gamma$ proportion of individuals that follow $F_{T1}$.

@@

For simplicity, we model total abundance at each survey $N_{s}$ using a Poisson distribution, though other non-negative integer-valued distributions may be used.  
We model the expected survey abundance $\lambda_{s}$ via mixed effects linear regression with a log link: $\log (\lambda_{s}) = \textbf{X}_{s}^A\boldsymbol{\beta}^A + \textbf{Z}_{s}^A\boldsymbol{\xi}^A$.  As with the detection model, $\textbf{X}_{s}^A$ are covariates, $\boldsymbol{\beta}^A$ is a vector of fixed effects, $\textbf{Z}_{s}^A$ specify random effect levels, and $\xi_i^A \overset{ind}{\sim} N(0,\sigma_{A[i]}^2)$ are random effects.  
We can decompose $N_{s}$ into observed and unobserved portions; the latent unobserved portion follows a binomial-Poisson hierarchy, with the result that $n_{s}^{(unobs)} \sim \mbox{Poisson}\left(\lambda_{s}(1-p_{s}^{(det)})\right)$.

@@

@@

@@

We selected priors to be non-informative within a reasonable range of values.  
Normal priors for the detection model intercept term, Intercept$^D$, were chosen so that, based on an intercept-only non-mixture model with scale parameter of 1: (i) median prior detection probability was $p_{s}^{(det)} = 0.50$, and (ii) 95\% of the prior detection probability was within $p_{s}^{(det)} \in (0.01, 1.0)$.  
Normal priors for Intercept$^A$ were centered at a median abundance of 3 birds per site and a 95\% probability of 0-14 birds present (counted and uncounted).  
Normal priors for effect parameters were centered at zero with standard deviations matching the appropriate intercept term.  
For all shape and variance parameters, we chose half-Cauchy(0,1) priors, and for the mixing parameter $\gamma$ we chose a Uniform(0,1) prior.  
All priors were independent.

To assess goodness of fit, we relied on posterior predictive checks \citep{Gelman1996}.  
Posterior predictive checks assess whether a fitted model can effectively replicate datasets that look like the original data in key aspects, which are measured by check statistics.  
In particular, we are concerned with the goodness of fit for the TTDD distribution, so we defined a check statistic for each observation interval:
\[D(n_i) = \sum\limits_{s} n_{si} \big/ \sum\limits_{si} n_{si}\]
which is the proportion of the total count that occurs during interval $i$ marginally across all surveys.  
The posterior predictive p-value associated with each $D(n_i)$ is the proportion of replicate check statistics that have a larger value than the check statistic for the actual data.  
We simulated replicate datasets and calculated the check statistic at each iteration of our MCMC sampling.  
Posterior predictive p-values near to 0 or 1 are potentially indicators of a misspecified model.

@@

We conducted three simulation studies to explore the behavior of models with non-constant TTDDs.
In Sim1, we compared models with detection heterogeneity (via a partial finite-mixture TTDD) versus models without detection heterogeneity.
We simulated both mixture and non-mixture datasets from exponential, gamma, lognormal, and Weibull TTDD families.  
Because model behavior may differ between peaked and non-peaked datasets, we simulated both for each TTDD family except exponential.  
Thus, combining mixtures, `peakedness' and TTDD families, we simulated datasets from 14 different TTDDs in total.  
In Sim2, we examined the impact of misspecifying the TTDD family (e.g., fitting an exponential TTDD model to data generated from a Weibull TTDD).  
Based on findings from Sim1, we considered only mixture TTDD datasets, and we fit each with mixture TTDD models from all four families.  
In Sim3, we modeled a more complete scenario where both data generation and model fitting included covariates and random effects for abundance and detection.

We used posterior median estimates from the Ovenbird analysis to inform simulation parameters except as follows.  
For Sim1 and Sim2, we chose true parameter values so that: (i) the overall expected detection probability was 0.80, (ii) for mixture datasets, $\gamma = 0.65$ (meaning 35\% of individuals were immediately detected), (iii) in non-peaked models, 70\% of \textit{detected} individuals were observed during the first two minutes, and (iv) in peaked models, the detection mode for `hard to detect' individuals occured at 5 minutes.  
For Sim3, all parameters used for non-peaked datasets came from the Ovenbird analysis, which produced only non-peaked model fits.
In order to simulate peaked dataset variants, we modified the Ovenbird parameters by:  (i) setting $\gamma = 0.65$, and (ii) scaling the Intercept$^D$ and $\sigma_D^2$ terms by 0.25 and 1.1, resulting on average in a detection mode near 5 minutes and 75-85\% overall detection across all sites.  
Unlike Sim1 and Sim2, detection probabilities in Sim3 were not the same for all datasets.
Counts were censored into nine-intervals as with the Ovenbird dataset.  
For both Sim1 and Sim2, we simulated 16 replicates, but for Sim3 we generated only a single replicate, because gamma models took an average of 5 days to fit.

YOU ARE HERE.  ADD A COMMENT ABOUT ABUNDANCE ESTIMATION.

@@

In the first simulation study, we simulated intercept-only datasets from 14 TTDDs and fit each with both the correctly specified model and one that was correct except for the mixture component (Table \ref{tbl:sim1}).  
When data derived from a mixture model, then inference models lacking a mixture component misestimated the detection probability $p^{(det)}$ badly in every case.  
This was particularly egregious when datasets feature peaked mixtures, where model coverage was always negligible.  
Conversely, when data derived from a non-mixture model, then inference models incorporating a mixture component performed as well as the true model.  
Indeed, for non-peaked non-mixture data, the mixture inference model provided more accurate posterior estimates of $p^{(det)}$ than the non-mixture inference model.  
The one exception was the exponential case, where both models estimated $p^{(det)}$ accurately, but the mixture inference model yielded credible intervals about 25\% wider than those from its mixture counterpart.
In most cases, model comparisons by DIC did not demonstrate a clear preference for the mixture model, even though non-mixture models displayed stronger bias and poorer coverage.

% Possible other comments
%(1) For non-peaked data, the true inference model is biased low\\
%(2) Mixture inference models generate higher estimates than non-mixture models\\
%(3) True models are generally good\\
%(4) Estimates of non-mixture peaked data are much more precise\\
%(5) Note that plots of TTDD at the median are indistinguishable from the truth except in the blatant fail scenario

\begin{table}[ht]\centering\small
\begin{tabular}{l|l|l|l|cccc|cccc||c}
 \multicolumn{4}{c|}{ } & \multicolumn{4}{c|}{\underline{Non-mixture model}} & \multicolumn{4}{c||}{\underline{Mixture model}} & \\
 \multicolumn{4}{c|}{ } & Med. $p$ & Q($p$) & 50\% & 90\% & Med. $p$ & Q($p$) & 50\% & 90\% & $\Delta$ DIC \\ 
  \hline
  \hline
 \parbox[t]{2mm}{\multirow{14}{*}{\rotatebox[origin=c]{90}{TTDD used to simulate data}}} & \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Non-mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.76 & 0.41 & 0.75 & 0.88 & 0.84 & 0.66 & 0.56 & 0.94 & 0.24 \\ 
 & & &   Lognormal & 0.66 & 0.17 & 0.31 & 0.62 & 0.78 & 0.48 & 0.62 & 1.00 & -0.67 \\ 
 & & &   Weibull & 0.69 & 0.25 & 0.38 & 0.75 & 0.79 & 0.51 & 0.75 & 1.00 & 0.37 \\ 
  \cline{3-13}
 & & &   Exponential & 0.80 & 0.54 & 0.44 & 0.94 & 0.79 & 0.38 & 0.31 & 0.88 & 1.48 \\ 
  \cline{3-13}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} &  Gamma & 0.80 & 0.55 & 0.50 & 1.00 & 0.82 & 0.70 & 0.38 & 0.88 & 0.96 \\ 
 & & &   Lognormal & 0.78 & 0.31 & 0.50 & 0.94 & 0.80 & 0.48 & 0.62 & 1.00 & 0.97 \\ 
 & & &   Weibull & 0.79 & 0.49 & 0.56 & 0.94 & 0.82 & 0.66 & 0.44 & 0.88 & 1.28 \\ 
  \cline{2-13}
& \parbox[t]{2mm}{\multirow{7}{*}{\rotatebox[origin=c]{90}{Mixture}}} & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Nonpk.}}} & Gamma & 0.67 & 0.17 & 0.12 & 0.81 & 0.76 & 0.41 & 0.69 & 1.00 & 0.51 \\ 
 & & &   Lognormal & 0.56 & 0.04 & 0.00 & 0.31 & 0.72 & 0.30 & 0.44 & 0.88 & 0.33 \\ 
 & & &   Weibull & 0.51 & 0.02 & 0.00 & 0.06 & 0.71 & 0.32 & 0.44 & 1.00 & 2.40 \\ 
  \cline{3-13}
 & & &   Exponential & 0.96 & 1.00 & 0.00 & 0.00 & 0.77 & 0.37 & 0.38 & 0.94 & 122.81 \\ 
  \cline{3-13}
 & & \parbox[t]{2mm}{\multirow{3}{*}{\rotatebox[origin=c]{90}{Peaked}}} & Gamma & 0.28 & 0.00 & 0.00 & 0.00 & 0.74 & 0.33 & 0.31 & 0.88 & 31.84 \\ 
 & & &   Lognormal & 0.22 & 0.00 & 0.00 & 0.00 & 0.76 & 0.36 & 0.38 & 0.94 & 63.65 \\ 
 & & &   Weibull & 0.22 & 0.00 & 0.00 & 0.00 & 0.70 & 0.29 & 0.56 & 0.94 & 28.30 \\ 
   \hline
\end{tabular}
\caption{\label{tbl:sim1} Summary of mixture vs. non-mixture model fits (Sim1).  
In all cases, the model family matches the dataset family.  
Med $p$: mean value across simulations of the posterior median of $p^{(det)}$ (true value = 0.80).  
Q($p$): proportion of the posterior distribution of $p^{(det)}$ that is larger than the true value on average.  
50\% and 90\% coverage is expressed as the proportion of 16 simulations for which the true value of $p^{(det)}$ lies within the appropriate credible interval.  
$\Delta$ DIC: mean difference in DIC between the incorrect-mixture model minus the true model. \adam{Thoughts on use of bold/italics to highlight some results?}}
\end{table}

\subsection{Sim2: Constant vs. non-constant detection TTDDs}\label{sec:family}

>>>>

A TTDD defines the range of detection patterns possible in an analysis.  
The most basic is an exponential TTDD, which imposes a constant first detection rate.  
Choosing another TTDD can allow for a systematic non-constant detection regime.  
For example, to model an observer effect where: (i) the observer's arrival suppresses or stimulates detectable cues, but (ii) organisms acclimate and gradually return to constant detection, a gamma TTDD could be appropriate.

Increasing hazard functions result in a pdf for $T$ that has a mode away from zero; we term these TTDDs `peaked'.  
We contrast these to decreasing hazard functions with a mode at zero, which we term `nonpeaked'.  
For our purposes, the exponential TTDD is neither peaked nor nonpeaked.

@@

@@

Our analysis is motivated by point-count surveys conducted in Chippewa National Forest from 2008-2013 as part of the Minnesota Forest Breeding Bird Project (MNFB).  
The MNFB design is described in \citet{Hanowski1995}, and we summarize only essential details here.  
Single-visit time-to-first-detection point-count surveys were conducted by trained observers at a fixed set of sampling locations once annually.  
Survey durations were 10 minutes, with times to first detection for over 50 species censored into nine intervals -- a two-minute interval followed by eight one-minute intervals.  
These relatively fine-scale intervals should provide more information about TTDDs than the three-interval methodology (0-3, 3-5, and 5-10 minutes) used in many avian point count surveys \citep{Ralph1995}.
There was no prescribed settling-in period between the observer's arrival and the time they began observing.

@@

We construct a hierarchical model of removal-sampled point-counts in three pieces: (a) a data model incorporating binomial detection and observed times to detection, (b) a detection model based upon a TTDD, and (c) an abundance model based upon an integer-valued count distribution.  
Our model incorporates covariates and random effects for both abundance and detection via mixed effects linear regression.

\subsection{Data Model}
We assume that counts from different surveys are conditionally independent.  
We define $T_{sq}$ as a random variable for the first time at which an individual is detected.
We assume that detection times for individuals at any given survey are independent, identically distributed according to a TTDD with cdf $F_T(t)$ and pdf $f_T(t)$, which may depend on covariates.  
The probability of detection for an animal is thus $p_{s}^{(det)} = F_T(C_I)$ and the conditional distribution of observed detection times can be written $f_{T|det}(t|t_{sq}<C_I) = f_T(t) \textbf{I}(t<C_I) / F_T(C_I)$.  
Denoting $N_{s}$ as the total number animals present at a survey, the data model is:
\begin{align}\label{eq:datamodel}
n_{s}^{(obs)} &\sim \mbox{Binomial}\left(N_{s}, p_{s}^{(det)}\right)\\
\label{eq:Tsrq}T_{sq} &\sim f_{T|det}(t|t_{sq}<C_I)
\end{align}
When detection times are censored, we replace Eq. \ref{eq:Tsrq} with $\vn_{s} \sim \mbox{Multinomial}\left(n_{s}^{(obs)}, \textbf{p}_{s}\right)$, where $\textbf{p}_{s}$ is the vector of interval-specific detection probabilities obtained by partitioning the conditional cdf $F_{T|det}(t|t_{sq}<C_I)$ at the interval cutoff times.  
It follows that $\sum_{i=1}^I p_{si} = 1$.

@@

The two main elements of the detection model for $T_{sq}$ are: (i) the distributional form and (ii) the expectation function.
$T_{sq}$ should be based on non-negative continuous distributions, preferrably featuring a rate parameter than can be estimated via regression.  
In this study, we adopt TTDDs for $T_{sq}$ using the following: Exponential($\varphi_{s}$), Gamma($\alpha, \varphi_{s}$), Weibull($k, \varphi_{s}$), and Lognormal($\mu_{s}, \sigma_{det}^2$).  
Here, $\varphi_{s}$ and $\mu_{s}$ are survey-specific detection rate parameters, and we consider the shape parameters $\alpha$, $k$, and $\sigma_{det}^2$ to be constant across all surveys.

We can model detection heterogeneity by defining $F_T(t)$ as a mixture of TTDD components.  
In this study, we use interval-censored observations, so in addition to the four above TTDDs (with no mixture component), we consider partial finite-mixtures of a point mass during the first survey interval plus a continuous component from an exponential, gamma, Weibull, or lognormal distribution.  
We define a constant mixing parameter $\gamma \in [0,1]$ for the proportion of animals not distributed according to the point mass.

We model the expectation function via mixed effects linear regression.  
For exponential, gamma, and Weibull TTDDs, we model: $\log(\varphi_{s}) = \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D$, where $\textbf{X}_{s}^D$ are covariates, $\boldsymbol{\beta}^D$ is a vector of fixed effects, $\textbf{Z}_{s}^D$ specifies random effect levels, $\xi_i^D \overset{ind}{\sim} N(0,\sigma_{D[i]}^2)$ are random effects, and $\sigma_{D[i]}^2$ denotes the variance associated with $\xi_i^D$.  
This regression is equivalent to modeling the log of the expected time-to-detection, which is inversely related to the detection rate.  
For the lognormal distribution, we fit the same regression model to $-\mu_{s}$.  
%Thus, the link functions in our detection model are:
%\begin{alignat}{3}
%&\text{Exponential:\;} &&\log(\varphi_{s}) &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}])\\
%&\text{Gamma:} &&\log(\varphi_{s}) &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}]) + \log(\alpha)\\
%&\text{Weibull:}  &&\log(\varphi_{s}) &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}]) + \log\left(\Gamma\left(1 + 1/k\right)\right)\\
%&\text{Lognormal:} &&-\mu_{s} &&= \text{Intercept}^D + \textbf{X}_{s}^D\boldsymbol{\beta}^D + \textbf{Z}_{s}^D\boldsymbol{\xi}^D = -\log(E[T_{sq}]) + \sigma_{det}^2/2
%\end{alignat}

Combining the distribution and expectation function for $T_{s}$, we can describe a partial-mixture TTDD cdf as:
\[F_T(t|\textbf{X}_{s}^D, \textbf{Z}_{s}^D, \boldsymbol{\theta}) = (1-\gamma)\mathbb{I}(t>0) + \gamma F_{T1}(t|\textbf{X}_{s}^D, \textbf{Z}_{s}^D, \boldsymbol{\theta})\]
where $F_{T1}$ is the cdf of the continuous component and $\boldsymbol{\theta}$ is a vector of parameters appropriate to $F_{T1}$.  
Note that parameters in a mixture TTDD do not share the exact same interpretation as equivalent parameters from a non-mixture TTDD, since they only pertain to the $\gamma$ proportion of individuals that follow $F_{T1}$.

@@

For simplicity, we model total abundance at each survey $N_{s}$ using a Poisson distribution, though other non-negative integer-valued distributions may be used.  
We model the expected survey abundance $\lambda_{s}$ via mixed effects linear regression with a log link: $\log (\lambda_{s}) = \textbf{X}_{s}^A\boldsymbol{\beta}^A + \textbf{Z}_{s}^A\boldsymbol{\xi}^A$.  As with the detection model, $\textbf{X}_{s}^A$ are covariates, $\boldsymbol{\beta}^A$ is a vector of fixed effects, $\textbf{Z}_{s}^A$ specifies random effect levels, and $\xi_i^A \overset{ind}{\sim} N(0,\sigma_{A[i]}^2)$ are random effects.  
We can decompose $N_{s}$ into observed and unobserved portions; the latent unobserved portion follows a binomial-Poisson hierarchy, with the result that $n_{s}^{(unobs)} \sim \mbox{Poisson}\left(\lambda_{s}(1-p_{s}^{(det)})\right)$.

@@

We selected priors to be non-informative within a reasonable range of values.  
Normal priors for the detection model intercept term, Intercept$^D$, were chosen so that, based on an intercept-only non-mixture model with scale parameter of one: (i) median prior detection probability was $p_{s}^{(det)} = 0.50$, and (ii) 95\% of the prior detection probability was within $p_{s}^{(det)} \in (0.01, 1.0)$.  
Normal priors for Intercept$^A$ were centered at a median abundance of 3 birds per site and a 95\% probability of 0-14 birds present (counted and uncounted).  
Normal priors for effect parameters were centered at zero with standard deviations matching the appropriate intercept term.  
For all shape and variance parameters, we chose half-Cauchy(0,1) priors, and for the mixing parameter $\gamma$ we chose a Uniform(0,1) prior.  
All priors were independent.

@@

\subsection{Model Fitting}

@@

To assess goodness of fit, we relied on posterior predictive checks \citep{Gelman1996}.  
Posterior predictive checks assess whether a fitted model can effectively replicate datasets that look like the original data in key aspects, which are measured by check statistics.  
In particular, we are concerned with the goodness of fit for the TTDD distribution, so we defined a check statistic for each observation interval:
\[D(n_i) = \sum\limits_{s} n_{si} \big/ \sum\limits_{si} n_{si}\]
which is the proportion of the total count that occurs during interval $i$ marginally across all surveys.  
The posterior predictive p-value associated with each $D(n_i)$ is the proportion of replicate check statistics that have a larger value than the check statistic for the actual data.  
Posterior predictive p-values near to 0 or 1 are potentially indicators of a misspecified model.
We simulated replicate datasets and calculated the check statistic at each iteration of our MCMC sampling.

@@

We conducted three simulation studies to explore the behavior of models with non-constant TTDDs.
In Sim1, we compared models with detection heterogeneity via a partial finite-mixture TTDD versus models without detection heterogeneity.
We simulated both mixture and non-mixture datasets from exponential, gamma, lognormal, and Weibull TTDD families.  
Because model behavior may differ between peaked and nonpeaked datasets, we simulated both for each TTDD family except exponential.  
Thus, combining mixtures, `peakedness' and TTDD families, we simulated datasets from 14 different TTDDs in total.  
In Sim2, we examined the impact of misspecifying the $F_{T1}$ family (e.g., fitting an exponential TTDD model to data generated from a Weibull TTDD).  
Of particular interest were scenarios with a time-varying $F_{T1}$ component in the data but a time-constant component in the inference model, and vice versa.
Based on findings from Sim1, we considered only mixture TTDD datasets, and we fit each with mixture TTDD models from all four families.  
In Sim3, we modeled a more complete scenario where both data generation and model fitting included covariates and random effects for abundance and detection.

We used posterior median estimates from the Ovenbird analysis to inform simulation parameters except as follows.  
For Sim1 and Sim2, we chose true parameter values so that: (i) the overall expected detection probability was 0.80, (ii) for mixture datasets, $\gamma = 0.65$ (meaning 35\% of individuals were immediately detected), (iii) in nonpeaked models, 70\% of \textit{detected} individuals were observed during the first two minutes, and (iv) in peaked models, the detection mode for `hard to detect' individuals occured at 5 minutes.  
For Sim3, all parameters used for nonpeaked datasets came from the Ovenbird analysis.
In order to simulate peaked dataset variants, we modified the Ovenbird parameters by:  (i) setting $\gamma = 0.65$, and (ii) scaling the Intercept$^D$ and $\sigma_D^2$ terms by 0.25 and 1.1, resulting on average in a detection mode near 5 minutes and 75-85\% overall detection across all sites.  
Unlike Sim1 and Sim2, expected detection probabilities in Sim3 were not the same for all datasets.
Counts were censored into nine-intervals as with the Ovenbird dataset.  
For both Sim1 and Sim2, we simulated 16 replicates, but for Sim3 we generated only a single replicate, because gamma models took an average of 5 days to fit.

@@

In Sim1, we simulated intercept-only datasets from 14 TTDDs and fit each with two models from the correct TTDD family: one allowing for detection heterogeneity in the form of a mixture component and one not (Table \ref{tbl:sim1}).  
When data derived from a mixture model, then inference models lacking a mixture component misestimated the detection probability $p^{(det)}$ badly in every case.  
This was particularly egregious for datasets featuring exponential and peaked mixtures, where non-mixture model coverage was always negligible.  
Conversely, when data derived from a non-mixture model, inference models incorporating a mixture component performed as well as the true model.  
Indeed, for nonpeaked non-mixture data, the mixture inference model provided more accurate posterior estimates of $p^{(det)}$ than did the true non-mixture inference model.  
The one case where the non-mixture model performed better was the non-mixture exponential dataset, where both inference models estimated $p^{(det)}$ accurately, but the mixture inference model yielded credible intervals about 25\% wider than those from its mixture counterpart.
Mixture model posterior medians for $p^{(det)}$ were always lower than non-mixture posterior medians for time-varying datasets and higher for exponential TTDDs.

\adam{Ack!  I'm having a Dickens of a time abbreviating the following paragraph.  I could use a hand.... maybe keep just the first sentence?}
Because abundance estimates are inversely related to detection estimates, they mirrored the observations for $p^{(det)}$ above and shared the same coverage rates.  
Median posterior abundance from mixture models was unbiased for non-mixture data and positively biased by only 4-15\% for mixture data.  
Median posterior abundance from non-mixture models applied to non-mixture data were unbiased (exponential and peaked) or biased by 5-24\% (nonpeaked); however, for mixture data, the non-mixture models were biased by 20-60\% (nonpeaked), -17\% (exponential), and 183-265\% (peaked).  
For the time-varying distributions, non-mixture models not only had greater bias, but 95\% credible intervals were generally 10-40\% wider (470\% wider for peaked mixture data).
For exponential datasets, the non-mixture model credible intervals were 28\% narrower for non-mixture data and an unrealistic 95\% narrower for mixture data.

Neither DIC nor posterior predictive checks indicated a clear preference for mixture models with nonpeaked data, even though non-mixture models displayed stronger bias and poorer coverage.  DIC did reveal a preference for mixture models with exponential and peaked datasets.  In these cases, posterior predictive checks clearly showed poor fit from the non-mixture models with p-values of 1.00 in the second and sometimes third observation intervals.  These p-values demonstrated that, relative to the observed data, the estimated TTDD placed too many counts during these intervals and too few in the first and later intervals.

% Possible other comments
%(1) For nonpeaked data, the true inference model is biased low\\
%(2) Mixture inference models generate higher estimates than non-mixture models\\
%(3) True models are generally good\\
%(4) Estimates of non-mixture peaked data are much more precise\\
%(5) Note that plots of TTDD at the median are indistinguishable from the truth except in the blatant fail scenario
